Lyman-alpha spectra from rotating outflows

### 2018-02-14 paper/paper.tex
edit

\begin{abstract}
We perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation. We reproduce the main features 
of the outcoming \lya line spectra with a simple semi-analytic model 
that modifies the spectra of outflows without rotation by adding a 
Doppler shift with the rotational information.

\end{abstract}

>>>>

\begin{abstract}
Outflows and rotation are two ubiquitous kinematic features in the gas
distributions of galaxies.
We perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation to understand how these two
features impact the morphology of the Lyman-$\alpha$ emission line.
One of the most notorious results is that rotation increases the
detected flux at the line's center in comparison with the
non-rotational case. 
Rotation also induces a line broadening and a dependency with the
viewing angle.
We present a semi-analytic model that modifies the spectra of
non-rotational that manages to reproduce the main features of these
Monte Carlo simulations. 
\end{abstract}
